\documentclass{beamer}

\begin{document}

\title{Recent developments in direct labeled graphics\\
  \url{http://directlabels.r-forge.r-project.org}}
\author{Toby Dylan Hocking \\ toby.hocking AT inria.fr}
\date{29 March 2012}

\frame{\titlepage}

\section{Motivation: confusing legends}

i.e. from the poster.

\section{How to add direct labels}

1. first try direct.label(p)

2. If that doesn't work check to see if another Positioning Method
exists on http://directlabels.r-forge.r-project.org/docs/index.html,
then use direct.label(p,"method")

3. If no Positioning Methods exist you can always write your own.

1---- examples: works well by default

http://directlabels.r-forge.r-project.org/docs/lineplot/plots/sexdeaths.html

http://directlabels.r-forge.r-project.org/docs/densityplot/plots/loci.html

http://directlabels.r-forge.r-project.org/docs/scatterplot/plots/iris.html

2---- examples: lineplot, scatterplot

lasso lineplot: try lasso.labels

bodyweight lineplot: try last.qp or first.qp

3---- examples: ... writing custom methods?

scatterplot: make numbers bigger
http://directlabels.r-forge.r-project.org/docs/scatterplot/plots/cylinders.html

ridge regression lineplot: space out using dl.trans
http://directlabels.r-forge.r-project.org/docs/lineplot/plots/ridge.html

lasso plot: add lasso.labels as well!
http://directlabels.r-forge.r-project.org/docs/lineplot/plots/lars.html

\section{How does it work?}

- lineplot QP

- scatterplot grid search

- drawing grid grobs with a custom drawDetails method. => window
resize updates, ggplot2 support

- generating a website using plots and methods defined in the R
package.

\section{Conclusions}

- directlabels is useful for everyday data visualization, but some
manual tweaking can help make a publication-quality figure.

- future work in image labels?

\end{document}
